Examples Compendium

### 2021-01-11 examples.tex
added tablaux equations to examples

\maketitle

% \section{Examples}
\section*{Disjoint, non-dominant $\mu$}

@@

\section*{Some multiplicity}

@@

For this example, I think we need $\lambda_1 = (2,0,0)$, $\lambda_2 = (2,2,0)$, $\mu_1 = (0,2,0)$, $\mu_2 = (2,0,2)$. Then 
\[
\left[\begin{BMAT}(e){cc;cc;cc}{cc;cc;cc} 
    0 & 1 & 0 & 0 & 0 & 0\\
    -s^2 & 2s & A_0 & A_1 & A_2 & A_3\\
    0 & 0 & 0 & 1 & 0 & 0\\
    0 & 0 & 0 & 0 & A_4 & A_5\\
    0 & 0 & 0 & 0 & 0 & 1\\
    0 & 0 & 0 & 0 & -s^2 & 2s
    \end{BMAT}\right]
\]

@@

\begin{comment}
\section*{Getting a feel for things}
\begin{example}
    Let 
    \[
    \begin{aligned}
        \mu_1 &= (2) & \lambda_1 &= & \mu &= (5) \\
        \mu_2 &= (3) & \lambda_2 &= & \lambda &= 
    \end{aligned}
    \]
    Consider the companion matrix $C(p)$ of 
    $$p(t) = (t-s)^3t^2 = (t^3 - 3t^2 s + 3t s^2 - s^3)t^2 = t^5 - 3 t^4 s + 3t^3 s^2 - t^2 s^3$$ 
    Let $X = C(p)^T$ so 
    \[
    X = \left[\begin{BMAT}(e){ccccc}{ccccc}
        0 & 1 & & & \\ 
        & 0 & 1 & & \\
        &   & 0 & 1 & \\ 
        &   &   & 0 & 1 \\
       0 & 0 & s^3 & -3s^2  & 3s  
    \end{BMAT}\right]    
    \]
    Ask that $X\big|_{E_0}$ has Jordan type $\lambda_1$ and $X-s\big|_{E_s}$ has Jordan type $\lambda_2$. In this rank 1 case we are forced to take $\lambda_i = \mu_i$.

@@

\section*{Simple root weights, things working}
\begin{example}
    Let 
    \[
    \begin{aligned}
        \mu_1 &= (3,1,1) & \lambda_1 &= (3,2,0) & \mu = (3,3,1) \\
        \mu_2 &= (0,2,0) & \lambda_2 &= (2,0,0) & \lambda = (5,2,0)
    \end{aligned}    
    \]
    and consider the companion matrices of 
    $$
    \begin{aligned}
        p_1(t) &= t^3 & p_2(t) &= t(t-s)^2 = t^3 - 2st^2 + s^2 t & p_3(t) &= t
    \end{aligned} % = t(t^2 - 2st + s^2) 
    $$
    \[
    X = \left[
        \begin{BMAT}(e){ccc;ccc;c}{ccc;ccc;c}
            0 & 1 & 0 & 0 & 0 & 0 & 0 \\
            0 & 0 & 1 & 0 & 0 & 0 & 0 \\
            % a & b & c & d & e & f & g \\ 
            0 & 0 & 0 & d & e & f & g \\ 
            0 & 0 & 0 & 0 & 1 & 0 & 0 \\
            0 & 0 & 0 & 0 & 0 & 1 & 0 \\
            0 & 0 & 0 & 0 & -s^2 & 2s & k \\
            0 & 0 & 0 & 0 & 0 & 0 & 0
        \end{BMAT}
        \right]    
    \]
    % \[
    %     \begin{BMAT}(e){ccc;ccc;c}{ccc;ccc;c} 
    %         0 & 1 & 0 & 0 & 0 & 0 & 0\\
    %         0 & 0 & 1 & 0 & 0 & 0 & 0\\
    %         0 & 0 & 0 & A_0 & A_1 & A_2 & A_3\\
    %         0 & 0 & 0 & 0 & 1 & 0 & 0\\
    %         0 & 0 & 0 & 0 & 0 & 1 & 0\\
    %         0 & 0 & 0 & 0 & -s^2 & 2*s & A_4\\
    %         0 & 0 & 0 & 0 & 0 & 0 & 0
    %     \end{BMAT}    
    % \]
\end{example}

@@

Equivalent linear algebra question(?): If $p(t,t-s) = p_1(t)p_2(t-s)$ then how are $C(p_1)$, $C(p_2)$, and $C(p)$ related? 
% I think the answer is basically this theorem \url{https://en.wikipedia.org/wiki/Structure_theorem_for_finitely_generated_modules_over_a_principal_ideal_domain} 
\newpage
\section*{Non simple root weights}
\begin{example}[Anne]
    Let $G = \SL_3$ and $\uvi = 121$.

>>>>

\maketitle
\tableofcontents

% \section{Examples}
\section{\today}
Let $Z$ be the MV cycle of weight $\alpha_3$ with Lusztig datum $(000,00,1)$ and $Z'$ the MV cycle of weight $\alpha_{1,2}$ with Lusztig datum $(010,00,0)$.

In terms of tableax the fusion $Z\ast Z'$ can be encoded as 
\begin{align}
    \young(1,2,4) \ast \young(3) &= \young(13,2,4) + \young(14,2,3) \\
    S_3 \ast (1\leftarrow 2) &= (1\leftarrow 2 \to 3) + P_3 \\ 
    (000,00,1)\ast (010,00,0) &= (010,00,1) + (001,00,0) \\
    &= (A_0 , A_5, A_1A_4 - A_2A_3) \sqcup (A_0 , A_1, A_3) 
\end{align}
where the ideals in line 3 are given in coordinates on matrices of the form
\[
    \left[\begin{BMAT}(e){c;c;c;c}{c;c;c;c} 
        0 & A_0 & A_1 & A_2\\
        0 & 0 & A_3 & A_4\\
        0 & 0 & s & A_5\\
        0 & 0 & 0 & 0
        \end{BMAT}\right]
\]

Next let $Z$ be the MV cycle of weight $\alpha_{1,3}$ having Lusztig datum $(100,01,0)$ and $Z'$ the MV cycle of weight $\alpha_2$ having Lusztig datum $(000,10,0)$.

Again, in terms of tableaux, $Z\ast Z'$ is given by 
\begin{align}
    \young(2,4) \ast \young(1,3) &= \young(13,24) + \young(12,34) \\
    (1\to 2\leftarrow 3) \ast S_2 &= P_2 + (2\leftarrow 3) \oplus (1 \to 2) \\
    (100,01,0) \ast (000,10,0) &= (010,01,0) + (100,11,0) 
\end{align}

TODO: fill in the ideals.

Now take $Z$ to be the MV cycle of weight $\alpha_{1,3}$ with Lusztig datum $(010,00,1)$ and leave $Z'$ as above. Then 
\begin{align}
    \young(13,2,4) \ast \young(11,23) &= \young(1113,223,4) + \young(1113,224,3) \\
    (1 \leftarrow 2 \to 3) \ast S_2 &= (2\to 3) \oplus (1\leftarrow 2) + P_2 \\
    (010,00,1) \ast (000,10,0) &= (010,10,1) + (010,01,0)
\end{align}
TODO: fill in the ideals.

Also computed: 
\begin{align}
    \young(1,2,4) \ast \young(12,3) &= \young(112,24,3) + \young(112,23,4) \\
    (000,00,1) \ast (100,10,0) &= (100,01,0) + (100,10,1) \\
    S_3 \ast (1\to 2) &= (1 \to 2 \leftarrow 3) + (1 \to 2 \to 3) \\
    &= (A_0,A_5,A_4,A_2) \sqcup (A_0,A_5,A_4,A_6) 
\end{align}
in 
\[
    \left[\begin{BMAT}(e){cc;cc;c;c}{cc;cc;c;c} 
        0 & 1 & 0 & 0 & 0 & 0\\
        0 & s & A_0 & A_1 & A_2 & A_3\\
        0 & 0 & 0 & 1 & 0 & 0\\
        0 & 0 & 0 & s & A_4 & A_5\\
        0 & 0 & 0 & 0 & s & A_6\\
        0 & 0 & 0 & 0 & 0 & 0
        \end{BMAT}\right]    
\]
TODO: add explanation, double check the ideals.

Finally, we guess that the fusion $2\alpha_1 \ast 2\alpha_2$ is encoded by the tableau equation 
\[
\young(22) \ast \young(11,33) = \young(1122,33) + \young(1123,23) + \young(1133,22)     
\]
Remains to check this and make sense of the middle term.

% 1
% 2 0 
% 2 1 0 
% 2 1 0 0

% 2
% 3 1 
% 3 1 1 
% 3 2 1 0

% 2 
% 3 1 
% 3 2 0 
% 3 2 1 0

\section{Disjoint, non-dominant weight}

@@

\section{Some multiplicity}

@@

For this example, I think we need $\lambda_1 = (2,0,0)$, $\lambda_2 = (2,2,0)$, $\mu_1 = (0,2,0)$, $\mu_2 = (2,0,2)$. 
\[
\yng(2) = \{\young(22)\} \qquad \yng(2,2) = \{\young(11,33)\} 
\]
Then 
\[
A = \left[\begin{BMAT}(e){cc;cc;cc}{cc;cc;cc} 
    0 & 1 & 0 & 0 & 0 & 0\\
    -s^2 & 2s & A_0 & A_1 & A_2 & A_3\\
    0 & 0 & 0 & 1 & 0 & 0\\
    0 & 0 & 0 & 0 & A_4 & A_5\\
    0 & 0 & 0 & 0 & 0 & 1\\
    0 & 0 & 0 & 0 & -s^2 & 2s
    \end{BMAT}\right]
\]
needs $A-s\big|_{\CC^2\cap E_s}$ has Jordan type $(2)$, $A\big|_{\CC^4\cap E_0}$ has Jordan type $(2)$, and $A-s\big|_{E_s}$ has Jordan type $(2,2)$. 
So 
\[
E_0 = \{A_0 \e_1 + s^2\e_3\leftarrow A_0 \e_2 + s^2 \e_4 + (A_0 + A_1 + \frac {2A_0}  s  ) \e_1 + s^2 \e_3 \}   
\]
while 
\begin{gather}
E_s^1 = \{\e_1 + s \e_2\leftarrow \e_1 + (1 + s) \e_2 \}  \\
E_s^2 = \{ -\frac{A_2 + sA_3}{A_0 + sA_1}\e_3 - \frac{sA_2 + s^2 A_3}{A_0 + sA_1} \e_4 + \e_5 + s \e_6  \leftarrow\}
\end{gather}
if 
\begin{gather}
    0 = A_4 + sA_5 \\
    \to A_0 A_4 \text{ as } s \to 0 
\end{gather}
and

@@

\begin{comment}
\section{Getting a feel for things}
\begin{example}
    Let 
    \[
    \begin{aligned}
        \mu_1 &= (2) & \lambda_1 &= & \mu &= (5) \\
        \mu_2 &= (3) & \lambda_2 &= & \lambda &= 
    \end{aligned}
    \]
    Consider the companion matrix $C(p)$ of 
    $$p(t) = (t-s)^3t^2 = (t^3 - 3t^2 s + 3t s^2 - s^3)t^2 = t^5 - 3 t^4 s + 3t^3 s^2 - t^2 s^3$$ 
    Let $X = C(p)^T$ so 
    \[
    X = \left[\begin{BMAT}(e){ccccc}{ccccc}
        0 & 1 & & & \\ 
        & 0 & 1 & & \\
        &   & 0 & 1 & \\ 
        &   &   & 0 & 1 \\
       0 & 0 & s^3 & -3s^2  & 3s  
    \end{BMAT}\right]    
    \]
    Ask that $X\big|_{E_0}$ has Jordan type $\lambda_1$ and $X-s\big|_{E_s}$ has Jordan type $\lambda_2$. In this rank 1 case we are forced to take $\lambda_i = \mu_i$.

@@

\section{Simple root weights, things working}
\begin{example}
    Let 
    \[
    \begin{aligned}
        \mu_1 &= (3,1,1) & \lambda_1 &= (3,2,0) & \mu = (3,3,1) \\
        \mu_2 &= (0,2,0) & \lambda_2 &= (2,0,0) & \lambda = (5,2,0)
    \end{aligned}    
    \]
    and consider the companion matrices of 
    $$
    \begin{aligned}
        p_1(t) &= t^3 & p_2(t) &= t(t-s)^2 = t^3 - 2st^2 + s^2 t & p_3(t) &= t
    \end{aligned} % = t(t^2 - 2st + s^2) 
    $$
    \[
    X = \left[
        \begin{BMAT}(e){ccc;ccc;c}{ccc;ccc;c}
            0 & 1 & 0 & 0 & 0 & 0 & 0 \\
            0 & 0 & 1 & 0 & 0 & 0 & 0 \\
            % a & b & c & d & e & f & g \\ 
            0 & 0 & 0 & d & e & f & g \\ 
            0 & 0 & 0 & 0 & 1 & 0 & 0 \\
            0 & 0 & 0 & 0 & 0 & 1 & 0 \\
            0 & 0 & 0 & 0 & -s^2 & 2s & k \\
            0 & 0 & 0 & 0 & 0 & 0 & 0
        \end{BMAT}
        \right]    
    \]
    % \[
    %     \begin{BMAT}(e){ccc;ccc;c}{ccc;ccc;c} 
    %         0 & 1 & 0 & 0 & 0 & 0 & 0\\
    %         0 & 0 & 1 & 0 & 0 & 0 & 0\\
    %         0 & 0 & 0 & A_0 & A_1 & A_2 & A_3\\
    %         0 & 0 & 0 & 0 & 1 & 0 & 0\\
    %         0 & 0 & 0 & 0 & 0 & 1 & 0\\
    %         0 & 0 & 0 & 0 & -s^2 & 2*s & A_4\\
    %         0 & 0 & 0 & 0 & 0 & 0 & 0
    %     \end{BMAT}    
    % \]
\end{example}

@@

Equivalent linear algebra question(?): If $p(t,t-s) = p_1(t)p_2(t-s)$ then how are $C(p_1)$, $C(p_2)$, and $C(p)$ related? 
% I think the answer is basically this theorem \url{https://en.wikipedia.org/wiki/Structure_theorem_for_finitely_generated_modules_over_a_principal_ideal_domain} 
\newpage
\section{Non simple root weights}
\begin{example}[Anne]
    Let $G = \SL_3$ and $\uvi = 121$.
